\chapter{Introduction}
As much as AI technology has been evolving rapidly over the past few decades, and its applications in the gaming industry are becoming more prevalent. Starting from making the enemies more aware of their surroundings, to making an infinite game with a real-time generated environment. This paper will talk about the development process of an AI that plays an indie game and evaluate its performance in comparison to human players. It will  analyze the:

\begin{enumerate}
\item Related work of the previous papers and projects that have been published about topics that are similar in neural network technologies.
\item Technologies that have been used to make this application come true.
\item Timeline for each (important) step was taken to make the game actually playable both by AI and a human with the physics behind particles, draw the components on the screen with a non-GUI library and creating genomes of AI.
\item Testing the AI with regard to parameters such as threshold and the highest score it can get after a specific period of training time. Explain the inputs it would get and how it will behave after changing each one.
\item Summary to see if the mentioned requirements have been satisfied or not.
\end{enumerate}

In summary, this paper will talk about the steps that are needed to make an AI that is capable of playing a game. In it, you will see a step-by-step explanation of how this is thought of, starting from the reason to have it in first place, to the ending result.
